Station summary

### 2023-02-15 reports/02_stations.qmd
Add zoop/physics maps

tar_load(c("zoop", "ant_sf"), store = here::here("_targets"))
source(here::here("R", "sp.R"))
source(here::here("R", "zoop.R"))
```

@@

zoop_sf <- latlon_to_sf(zoop, 
                        coords = c("dec.longitude", "dec.latitude")) %>% 
  sf::st_transform(ant_proj())

@@

>>>>

tar_load(c("zoop_sf", "ant_sf"), store = here::here("_targets"))
source(here::here("R", "sp.R"))
source(here::here("R", "zoop.R"))
```

@@

@@

## Zooplankton community/physics maps

```{r}
#| label: zoop_physics_maps

zoop_physics_vars <- c("Winter Cluster factor",
                       "Net.ice.type",
                       "Net.ice.percent",
                       "zuml_m",
                       "avg.Dens.Diff",
                       "avg.salinity",
                       "avg.temp",
                       "Water.Zone",
                       "Integ.chla.zuml",
                       "Integ.phae.zuml",
                       "Integ.chla.100m",
                       "Integ.phae.100m")

station_map <- function(var) {
  ant_basemap(map_lim) +
    geom_sf(aes(color = .data[[var]]), zoop_sf, size = 2, shape = 15) +
    facet_wrap(~ Year) +
    scale_x_continuous(breaks = c(-60, -55)) +
    scale_y_continuous(breaks = c(-63, -62, -61, -60)) +
    coord_ant(map_lim) +
    theme(legend.position = "bottom")
}

walk(zoop_physics_vars, compose(print, station_map))

```
